Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-06-13 paper/paper.tex
Wrong word

For CP models, using a branching rule for correctness, rather than simply as an ordering heuristic,
is unconventional and does not cleanly fit into the abstractions used by toolkits. However, we saw
that combining conventional filtering and the special branching rule was beneficial.

>>>>

For CP models, using a branching rule for connectedness, rather than simply as an ordering heuristic,
is unconventional and does not cleanly fit into the abstractions used by toolkits. However, we saw
that combining conventional filtering and the special branching rule was beneficial.
